A Domain-Specific Optimizing Compiler\\for Solving Partial Differential Equations

### 2014-03-10 paper/bare_conf.tex
Add cost model description. Change cost model algo. Minor refactoring.

We focus on Local Assembly (``assembly'', in the following), a fundamental step of a Finite Element Method that covers an important fraction of the overall computation run-time, typically in the range 30$\%$-60$\%$. During the assembly phase, the solution of the PDE is approximated by executing a suitable kernel over all elements in the discretized domain. A kernel's working set is usually small enough to fit the L1 cache; it might need L2 cache when high-order methods are employed to improve the accuracy of the solution. However, we do not consider the latter case. An assembly kernel is characterized by the presence of an affine, usually non-perfect loop nest, where individual loops are rather small (the trip count rarely exceeds 40, with a minimum value of 3, depending on the order of the method). With such small kernels, we focus on aspects like minimization of floating-point operations, register allocation and instruction-level parallelism, especially in the form of SIMD vectorization. Our study is conducted in the context of Firedrake, a system for solving PDEs through the Finite Element Method based on the OP2 abstraction~\cite{firedrake}.

@@

\section{Domain-Driven Code Transformations}
\label{sec:code-transf}
%All the work done in the polyhedral model should be useful, but our kernels fit L1, so they need special attention for what concerns key aspects like managing registers, exploiting ILP in its various forms, and reducing loop overhead. 
%Follows a description of code transformations using our compiler-driven approach.

@@

% Autovectorizable LICM -> show code snippet?
\subsection{Auto-vectorizable Loop-invariant Code Motion}
From inspection of the codes in Figures~\ref{code:helmholtz} and~\ref{code:burgers}, it can be noticed that the computation of $A$ involves evaluating many sub-expressions that depend on two iteration variables only. Since symbols in most of these sub-expressions are read-only variables, there is ample space for loop-invariant code motion. Vendor compilers apply this technique, although not in the systematic way we need for our assembly kernels. We want to overcome two deficiencies that both $icc$ and $gcc$ have. First, these compilers can identify sub-expressions that are invariant with respect to the innermost loop only. This is an issue for sub-expressions depending on $i$-$k$, which are not automatically lifted. Second, the hoisted code is scalar, i.e. it is not subjected to auto-vectorization. We work around these limitations with source-level loop-invariant code motion. In particular, we pre-compute all values that an invariant sub-expression assumes along the fastest varying dimension. This is implemented by introducing a temporary array (per invariant sub-expression) and by adding a new loop to the nest. At the price of extra memory for storing temporaries, the gain is that lifted terms can be auto-vectorized, because part of an inner loop. Given the short trip counts of our loops, it is important to achieve auto-vectorization of hoisted terms in order to minimize the percentage of scalar instructions, which could be otherwise significant. It is also worth noting that, in some problems, invariant sub-expressions along $j$ are identical to those along $k$ (e.g. in Helmholtz). In these cases, we safely avoid redundant pre-computation since, as anticipated in Section~\ref{sec:background}, a property of our domain is that $j$ and $k$ loops share the same iteration space.

@@

% Register allocation and register locality
\subsection{Optimizing Register Management}
One notable problem assembly kernels are exposed to concerns register allocation and register locality. The critical situation occurs when loop trip counts and accessed variables are such that the vector-registers pressure is high. Due to a kernel's working set fitting the L1 cache, it is remarkably important to optimize register management. Canonical optimizations, such as loop interchange, unroll, unroll-and-jam and register tiling are typically employed to deal with this problem. In the compiler we have developed, we support these optimizations either by means of explicit source code transformation (interchange, unroll-and-jam) or indirectly advising the compiler through standard pragmas (unroll). 
In this context, register tiling is a critical optimization. A way of obtaining register tiles consists of slicing the innermost loop into rectangular blocks of identical size (except the ``reminder'' block), and applying unrolling to individual blocks in order to expose ILP. This is automated by some vendor compilers~\cite{comdex}. Register tiles along both inner dimensions can be determined as well. Based on the observation that the evaluation of the stiffness matrix can be reduced to a ``summation of outer products'' along the $j$ and $k$ dimensions, we implement a domain-specific vector-register tiling strategy that leads to larger tiles, enhancing reuse. If we consider the code snippet in Figure~\ref{code:helmholtz-licm} (Helmholtz after loop-invariant code motion), we can notice that the computation of $A$ is abstractly expressible as
\begin{equation}
\label{outer-product}
A_{jk} = \sum_{\substack{
  x \in B' \subseteq B \\ 
  y \in B'' \subseteq B}} 
x_j\cdot y_k ~~~~~~ j,k = 0,...,4
\end{equation}
where $B$ is the set of all matrices (or temporaries) accessed in the kernel, whereas $B'$ and $B''$ are generic problem-dependent subsets. Without loss of generality, the presence of constants or other variables independent of both $j$ and $k$ can be momentarily neglected. Note that regardless of the specific input problem, the stiffness matrix computation is always reducible to this kind of form. Figure~\ref{fig:vect-by-vect} illustrates how we can evaluate 16 elements ($j,k=0,...,4$) of the stiffness matrix using just 2 vector registers (a 4$\times$4 tile), assuming $\vert B' \vert = \vert B'' \vert = 1$. Values in a register are shuffled each time a product is performed. Standard compiler auto-vectorization ($gcc$ and $icc$), instead, executes 4 broadcast operations (i.e. ``splat'' of a value over all of the register locations) along the outer dimension to perform the calculation, and would also need to keep between $f=1$ and $f=3$ extra registers to perform the same 16 evaluations when unroll-and-jam is used, with $f$ being the unroll-and-jam factor.

@@

The compiler structure is outlined in Figure~\ref{algo:PyOP2Compiler}. Initially, an AST is inspected, looking for the presence of iteration spaces and other domain-specific information provided by the higher layer. If the kernel lacks an iteration space, then so-called inter-kernel vectorization, in which the non-affine loop over mesh elements is vectorized, can be applied. This feature, currently under development, has been proved to be useful in several Finite-Volume-based applications~\cite{reguly-inter-kernel}. The second transformation step is applied if the backend is a manycore machine, like a GPU: the compiler tries to extract parallelism from inside the kernel, by partitioning loop iterations among different threads, if these are found to be independent~\cite{quadrature-cuda}. Then, an ordered sequence of optimization steps are executed. Application of $licm$ must precede padding and data alignment, due to the introduction of temporary arrays. Based on a cost model, the $split$, and subsequently the $op$-$vect$, transformations may be introduced. The compiler handles any possible corner cases: for example, if $op$-$vect$ is to be applied but the size of the iteration space is not a multiple of the vector length, then a reminder loop, amenable to auto-vectorization, is inserted.

Loop unroll and unroll-and-jam of outer loops are fundamental to expose ILP and data reuse, and so tuning critical parameters such as the unroll factor becomes of great importance. Autotuning might be used, although we avoid it to minimize the overhead of Firedrake's just-in-time compilation. It is our experience (inspection of assembly code, comparison with other hand-made implementations), however, that for our assembly kernels, where the loop nest is affine, bounds are known at compile-time, and memory accesses are unit-stride, newest versions of a vendor compiler like $icc$ employ cost models capable of estimating close-to-optimal values for such parameters.  We therefore leave the backend compiler in charge to select unroll and unroll-and-jam factors. This choice also simplifies the compiler's cost model. The only situation in which we explicitly unroll-and-jam a loop is when $op$-$vect$ is used, since the transformed code seems to prevent the $icc$ compiler from applying loop unrolling, even if specific pragmas are added.

@@

The cost model ..... TODO

\begin{algorithm}[t]
\caption{Procedure to estimate the most suitable unroll-and-jam factor and/or split size.}
\label{algo:applyCostModel}
  \textbf{Algorithm: ApplyCostModel}\\
  \KwIn{n\_inner\_arrays, n\_regs}
  \KwOut{uaj\_factor, sz\_split}

%// roundup(A, B) is a function that rounds A up to the nearest multiple of B \\

sz\_split = 0 \\
// Compute spltting factor \\
\While{n\_inner\_arrays $>$ n\_regs}{
  n\_inner\_arrays = n\_inner\_arrays / 2 \\
  sz\_split = sz\_split + 1 
}

n\_inner\_regs = n\_regs / 2 \\
\If{n\_inner\_arrays $>$ n\_inner\_regs \KwSty{or} sz\_split $>$ 0}{
  // Rely on autovectorization, as there might be not enough registers to improve performance by tiling \\
  \Return{$<$sz\_split, 0$>$}
}

// Compute unroll-and-jam factor for vector-register tiling \\
n\_regs\_avail = n\_regs - n\_inner\_arrays \\
uaj\_factor = $\lceil$n\_reg\_avail / n\_inner\_arrays$\rceil$ \\
\Return{$<$sz\_split, uaj\_factor$>$}
\end{algorithm}

Mention heuristic used by our compiler for splitting.. TODO

@@

%\newcommand{\massmatrixtwodresultsnorms}{
%\begin{tabularx}{1.0\textwidth}{c|XX|XX|XX|XX|}
%\cline{2-9}
%& \multicolumn{2}{c|}{$n_f=1$} & \multicolumn{2}{c|}{$n_f=2$} & \multicolumn{2}{c|}{$n_f=3$} & \multicolumn{2}{c|}{$n_f=4$} \\
%\cline{2-9}
%& A & Tensor& A & Tensor& A & Tensor& A & Tensor\\
%\hline
%\multicolumn{1}{|c|}{$p=1,q=1$} & $6.89e{-}17$ & $9.30e{-}17$ & $5.49e{-}17$ & $4.95e{-}17$ & $1.44e{-}17$ & $1.34e{-}17$ & $1.56e{-}17$ & $\mathbf{4.43e{-}5}$ \\
%\multicolumn{1}{|c|}{$p=1,q=2$} & $6.80e{-}17$ & $1.56e{-}16$ & $1.22e{-}16$ & $7.14e{-}17$ & $1.17e{-}17$ & $1.27e{-}17$ & $8.05e{-}18$ & $\mathbf{9.77e{-}5}$ \\
%\multicolumn{1}{|c|}{$p=1,q=3$} & $8.16e{-}17$ & $8.94e{-}17$ & $6.21e{-}17$ & $\mathbf{6.77e{-}5}$ & $2.44e{-}17$ & $\mathbf{7.69e{-}4}$ & $8.61e{-}17$ & $\mathbf{5.02e{-}4}$ \\
%\multicolumn{1}{|c|}{$p=1,q=4$} & $3.70e{-}16$ & $\mathbf{1.83e{-}4}$ & $7.12e{-}16$ & $\mathbf{4.11e{-}4}$ & $2.65e{-}16$ & $\mathbf{5.42e{-}4}$ & $5.03e{-}16$ & $\mathbf{4.36e{-}4}$ \\
%\hline
%\multicolumn{1}{|c|}{$p=2,q=1$} & $2.42e{-}16$ & $2.34e{-}16$ & $1.18e{-}16$ & $3.42e{-}17$ & $2.78e{-}17$ & $\mathbf{1.30e{-}4}$ & $1.22e{-}16$ & $\mathbf{3.06e{-}4}$ \\
%\multicolumn{1}{|c|}{$p=2,q=2$} & $4.50e{-}16$ & $1.47e{-}16$ & $7.47e{-}17$ & $\mathbf{7.04e{-}5}$ & $4.05e{-}16$ & $\mathbf{6.47e{-}4}$ & - & - \\
%\multicolumn{1}{|c|}{$p=2,q=3$} & $1.85e{-}16$ & $\mathbf{1.65e{-}4}$ & $7.76e{-}16$ & $\mathbf{5.57e{-}4}$ & $1.88e{-}15$ & $\mathbf{1.47e{-}3}$ & - & - \\
%\multicolumn{1}{|c|}{$p=2,q=4$} & $2.22e{-}15$ & $\mathbf{2.90e{-}4}$ & $4.01e{-}15$ & $\mathbf{1.42e{-}3}$ & - & - & - & - \\
%\hline
%\multicolumn{1}{|c|}{$p=3,q=1$} & $6.54e{-}17$ & $5.96e{-}17$ & $8.13e{-}17$ & $\mathbf{9.70e{-}5}$ & - & - & - & - \\
%\multicolumn{1}{|c|}{$p=3,q=2$} & $9.43e{-}17$ & $1.26e{-}16$ & $8.99e{-}16$ & $\mathbf{5.23e{-}4}$ & - & - & - & - \\
%\multicolumn{1}{|c|}{$p=3,q=3$} & $2.27e{-}16$ & $\mathbf{2.86e{-}4}$ & $5.77e{-}15$ & $\mathbf{1.81e{-}3}$ & - & - & - & - \\
%\multicolumn{1}{|c|}{$p=3,q=4$} & $2.45e{-}15$ & $\mathbf{5.31e{-}4}$ & $1.62e{-}14$ & $\mathbf{2.54e{-}3}$ & - & - & - & - \\
%\hline
%\end{tabularx}
%}
%\begin{figure*}
%\massmatrixtwodresultsnorms
%\end{figure*}

>>>>

We focus on Local Assembly (``assembly'', in the following), a fundamental step of a Finite Element Method that covers an important fraction of the overall computation run-time, typically in the range 30$\%$-60$\%$. During the assembly phase, the solution of the PDE is approximated by executing a suitable kernel over all elements in the discretized domain. A kernel's working set is usually small enough to fit the L1 cache; it might need L2 cache when high-order methods are employed to improve the accuracy of the solution. However, we do not consider the latter case. An assembly kernel is characterized by the presence of an affine, usually non-perfect loop nest, where individual loops are rather small (the trip count rarely exceeds 30, with a minimum value of 3, depending on the order of the method). With such small kernels, we focus on aspects like minimization of floating-point operations, register allocation and instruction-level parallelism, especially in the form of SIMD vectorization. Our study is conducted in the context of Firedrake, a system for solving PDEs through the Finite Element Method based on the OP2 abstraction~\cite{firedrake}.

@@

\section{Code Transformations}
\label{sec:code-transf}
%All the work done in the polyhedral model should be useful, but our kernels fit L1, so they need special attention for what concerns key aspects like managing registers, exploiting ILP in its various forms, and reducing loop overhead. 
%Follows a description of code transformations using our compiler-driven approach.

@@

% Autovectorizable LICM -> show code snippet?
\subsection{Domain-driven Loop-invariant Code Motion}
From inspection of the codes in Figures~\ref{code:helmholtz} and~\ref{code:burgers}, it can be noticed that the computation of $A$ involves evaluating many sub-expressions that depend on two iteration variables only. Since symbols in most of these sub-expressions are read-only variables, there is ample space for loop-invariant code motion. Vendor compilers apply this technique, although not in the systematic way we need for our assembly kernels. We want to overcome two deficiencies that both $icc$ and $gcc$ have. First, these compilers can identify sub-expressions that are invariant with respect to the innermost loop only. This is an issue for sub-expressions depending on $i$-$k$, which are not automatically lifted. Second, the hoisted code is scalar, i.e. it is not subjected to auto-vectorization. We work around these limitations with source-level loop-invariant code motion. In particular, we pre-compute all values that an invariant sub-expression assumes along the fastest varying dimension. This is implemented by introducing a temporary array (per invariant sub-expression) and by adding a new loop to the nest. At the price of extra memory for storing temporaries, the gain is that lifted terms can be auto-vectorized, because part of an inner loop. Given the short trip counts of our loops, it is important to achieve auto-vectorization of hoisted terms in order to minimize the percentage of scalar instructions, which could be otherwise significant. It is also worth noting that, in some problems, invariant sub-expressions along $j$ are identical to those along $k$ (e.g. in Helmholtz). In these cases, we safely avoid redundant pre-computation since, as anticipated in Section~\ref{sec:background}, a property of our domain is that $j$ and $k$ loops share the same iteration space.

@@

% Register allocation and register locality
\subsection{Domain-drive Optimization of Register Management}
One notable problem assembly kernels are exposed to concerns register allocation and register locality. The critical situation occurs when loop trip counts and accessed variables are such that the vector-registers pressure is high. Due to a kernel's working set fitting the L1 cache, it is remarkably important to optimize register management. Canonical optimizations, such as loop interchange, unroll, unroll-and-jam and register tiling are typically employed to deal with this problem. In the compiler we have developed, we support these optimizations either by means of explicit source code transformation (interchange, unroll-and-jam) or indirectly advising the compiler through standard pragmas (unroll). 
In this context, register tiling is a critical optimization. A way of obtaining register tiles consists of slicing the innermost loop into rectangular blocks of identical size (except the ``reminder'' block), and applying unrolling to individual blocks in order to expose ILP. This is automated by some vendor compilers~\cite{comdex}. Register tiles along both inner dimensions can be determined as well. Based on the observation that the evaluation of the stiffness matrix can be reduced to a ``summation of outer products'' along the $j$ and $k$ dimensions, we implement a domain-specific vector-register tiling strategy that leads to larger tiles, enhancing reuse. If we consider the code snippet in Figure~\ref{code:helmholtz-licm} (Helmholtz after loop-invariant code motion), we can notice that the computation of $A$ is abstractly expressible as
\begin{equation}
\label{outer-product}
A_{jk} = \sum_{\substack{
  x \in B' \subseteq B \\ 
  y \in B'' \subseteq B}} 
x_j\cdot y_k ~~~~~~ j,k = 0,...,4
\end{equation}
where $B$ is the set of all matrices (or temporaries) accessed in the kernel, whereas $B'$ and $B''$ are generic problem-dependent subsets. Without loss of generality, the presence of constants or other variables independent of both $j$ and $k$ can be momentarily neglected. Note that regardless of the specific input problem, the stiffness matrix computation is always reducible to this kind of form. Figure~\ref{fig:vect-by-vect} illustrates how we can evaluate 16 elements ($j,k=0,...,4$) of the stiffness matrix using just 2 vector registers (a 4$\times$4 tile), assuming $\vert B' \vert = \vert B'' \vert = 1$. Values in a register are shuffled each time a product is performed. Standard compiler auto-vectorization ($gcc$ and $icc$), instead, executes 4 broadcast operations (i.e. ``splat'' of a value over all of the register locations) along the outer dimension to perform the calculation, and would also need to keep between $f=1$ and $f=3$ extra registers to perform the same 16 evaluations when unroll-and-jam is used, with $f$ being the unroll-and-jam factor.

@@

The compiler structure is outlined in Figure~\ref{algo:PyOP2Compiler}. Initially, an AST is inspected, looking for the presence of iteration spaces and other domain-specific information provided by the higher layer. If the kernel lacks an iteration space, then so-called inter-kernel vectorization, in which the non-affine loop over mesh elements is vectorized, can be applied. This feature, currently under development, has been proved to be useful in several Finite-Volume-based applications~\cite{reguly-inter-kernel}. The second transformation step is applied if the backend is a manycore machine, like a GPU: the compiler tries to extract parallelism from inside the kernel, by partitioning loop iterations among different threads, if these are found to be independent~\cite{quadrature-cuda}. Then, an ordered sequence of optimization steps are executed. Application of $licm$ must precede padding and data alignment, due to the introduction of temporary arrays. Based on a cost model, the $split$ and $op$-$vect$ transformations may be introduced; their implementation is based on analysis and trasformation of the AST. The compiler handles any possible corner cases: for example, if $op$-$vect$ is to be applied but the size of the iteration space is not a multiple of the vector length, then a reminder loop, amenable to auto-vectorization, is inserted.

The cost model is shown in Figure~\ref{algo:applyCostModel}. It takes into account the number of available vector registers ($n\_regs$) and the number of variables iterating along the $j$ and $k$ dimensions ($n\_consts$ for independent variables, $n\_outer\_arrays$ for $j$ variables, and $n\_inner\_arrays$ for $k$ variables, assuming the $ijk$ loop order) to estimate unroll-and-jam and split factors when, respectively, $op$-$vect$ and $split$ are used (if a factor is 0, then the corresponding transformation is not applied). The $split$ transformation is triggered whenever the number of hoistable terms is larger than the available registers along the outer dimension (lines 3-8), which is approximated as half of the total (line 2). A split factor of $n$ means that the assembly expression should be ``cut'' into $n$ sub-expressions. Depending on the structure of the assembly expression, each sub-expression might end up accessing a different number of arrays; the cost model is simplified by assuming that all sub-expressions are of the same size. Finally, the unroll-and-jam factor for the $op$-$vect$ transformation is determined as a function of ``free'' registers, i.e. those not used for keeping hoisted terms (line 9-11).

Loop unroll and unroll-and-jam of outer loops are fundamental to expose ILP and data reuse, and so tuning critical parameters such as the unroll factor becomes of great importance. Autotuning might be used, although we avoid it to minimize the overhead of Firedrake's just-in-time compilation. It is our experience (inspection of assembly code, comparison with other hand-made implementations), however, that for our assembly kernels, where the loop nest is affine, bounds are known at compile-time, and memory accesses are unit-stride, newest versions of a vendor compiler like $icc$ employ cost models capable of estimating close-to-optimal values for such parameters.  We therefore leave the backend compiler in charge to select unroll and unroll-and-jam factors. This choice also simplifies the compiler's cost model. The only situation in which we explicitly unroll-and-jam a loop is when $op$-$vect$ is used, since the transformed code seems to prevent the $icc$ compiler from applying unroll-based optimizations, even if specific pragmas are added.

@@

\begin{algorithm}[t]
\caption{The cost model is employed by the compiler to estimate the most suitable unroll-and-jam (when $op$-$vect$ is used) and split factors, avoiding the overhead of auto-tuning.}
\label{algo:applyCostModel}
  \textbf{Cost Model}\\
  \KwIn{n\_outer\_arrays, n\_inner\_arrays, n\_consts, n\_regs}
  \KwOut{uaj\_factor, split\_factor}

n\_outer\_regs = n\_regs / 2 \\
split\_factor = 0 \\ 
// Compute spltting factor \\
\While{n\_outer\_arrays $>$ n\_outer\_regs}{
  n\_outer\_arrays = n\_outer\_arrays / 2 \\
  split\_factor = split\_factor + 1 
}

// Compute unroll-and-jam factor for $op$-$vect$ \\
n\_regs\_avail = n\_regs - (n\_outer\_arrays + n\_consts)\\
uaj\_factor = $\lceil$n\_reg\_avail / n\_inner\_arrays$\rceil$ \\
\Return{$<$split\_factor, uaj\_factor$>$}
\end{algorithm}

@@

\newcommand{\massmatrixtwodresultsnorms}{
\begin{tabularx}{1.0\textwidth}{c|XX|XX|XX|XX|}
\cline{2-9}
& \multicolumn{2}{c|}{$n_f=1$} & \multicolumn{2}{c|}{$n_f=2$} & \multicolumn{2}{c|}{$n_f=3$} & \multicolumn{2}{c|}{$n_f=4$} \\
\cline{2-9}
& A & Tensor& A & Tensor& A & Tensor& A & Tensor\\
\hline
\multicolumn{1}{|c|}{$p=1,q=1$} & $6.89e{-}17$ & $9.30e{-}17$ & $5.49e{-}17$ & $4.95e{-}17$ & $1.44e{-}17$ & $1.34e{-}17$ & $1.56e{-}17$ & $\mathbf{4.43e{-}5}$ \\
\multicolumn{1}{|c|}{$p=1,q=2$} & $6.80e{-}17$ & $1.56e{-}16$ & $1.22e{-}16$ & $7.14e{-}17$ & $1.17e{-}17$ & $1.27e{-}17$ & $8.05e{-}18$ & $\mathbf{9.77e{-}5}$ \\
\multicolumn{1}{|c|}{$p=1,q=3$} & $8.16e{-}17$ & $8.94e{-}17$ & $6.21e{-}17$ & $\mathbf{6.77e{-}5}$ & $2.44e{-}17$ & $\mathbf{7.69e{-}4}$ & $8.61e{-}17$ & $\mathbf{5.02e{-}4}$ \\
\multicolumn{1}{|c|}{$p=1,q=4$} & $3.70e{-}16$ & $\mathbf{1.83e{-}4}$ & $7.12e{-}16$ & $\mathbf{4.11e{-}4}$ & $2.65e{-}16$ & $\mathbf{5.42e{-}4}$ & $5.03e{-}16$ & $\mathbf{4.36e{-}4}$ \\
\hline
\multicolumn{1}{|c|}{$p=2,q=1$} & $2.42e{-}16$ & $2.34e{-}16$ & $1.18e{-}16$ & $3.42e{-}17$ & $2.78e{-}17$ & $\mathbf{1.30e{-}4}$ & $1.22e{-}16$ & $\mathbf{3.06e{-}4}$ \\
\multicolumn{1}{|c|}{$p=2,q=2$} & $4.50e{-}16$ & $1.47e{-}16$ & $7.47e{-}17$ & $\mathbf{7.04e{-}5}$ & $4.05e{-}16$ & $\mathbf{6.47e{-}4}$ & - & - \\
\multicolumn{1}{|c|}{$p=2,q=3$} & $1.85e{-}16$ & $\mathbf{1.65e{-}4}$ & $7.76e{-}16$ & $\mathbf{5.57e{-}4}$ & $1.88e{-}15$ & $\mathbf{1.47e{-}3}$ & - & - \\
\multicolumn{1}{|c|}{$p=2,q=4$} & $2.22e{-}15$ & $\mathbf{2.90e{-}4}$ & $4.01e{-}15$ & $\mathbf{1.42e{-}3}$ & - & - & - & - \\
\hline
\multicolumn{1}{|c|}{$p=3,q=1$} & $6.54e{-}17$ & $5.96e{-}17$ & $8.13e{-}17$ & $\mathbf{9.70e{-}5}$ & - & - & - & - \\
\multicolumn{1}{|c|}{$p=3,q=2$} & $9.43e{-}17$ & $1.26e{-}16$ & $8.99e{-}16$ & $\mathbf{5.23e{-}4}$ & - & - & - & - \\
\multicolumn{1}{|c|}{$p=3,q=3$} & $2.27e{-}16$ & $\mathbf{2.86e{-}4}$ & $5.77e{-}15$ & $\mathbf{1.81e{-}3}$ & - & - & - & - \\
\multicolumn{1}{|c|}{$p=3,q=4$} & $2.45e{-}15$ & $\mathbf{5.31e{-}4}$ & $1.62e{-}14$ & $\mathbf{2.54e{-}3}$ & - & - & - & - \\
\hline
\end{tabularx}
}
\begin{figure*}
\massmatrixtwodresultsnorms
\end{figure*}
